Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-07-13 documentation/userguide.tex
New arrangement of the tests directory, to more closely reflect the fact that our tests are now either tests of our problem or problems in the CASTRO test suite.

\begin{itemize}
  \item The \texttt{gravity} subdirectory includes problems that test the Poisson 
self-gravity module in CASTRO.
  \begin{itemize}
    \item The \texttt{boundary\_condition\_comparison} test checks the validity of our 
multipole approximation for the boundary conditions on the Poisson equation. It runs
the gravity solve for several different choices of the number of expansion coefficients
and compares the resulting gravitational potential to the exact result.
    \item The \texttt{uniform\_cube\_sphere} test is designed to check the convergence
properties of the Poisson solver. It loads either a sphere or cube of uniform density
onto the computational domain and then calculates the potential at several different
spatial resolutions to check if the potential converges.
  \end{itemize}
  \item The \texttt{hydro} subdirectory tests includes tests that use the hydrodynamics 
module, including many with self-gravity.
  \begin{itemize}
    \item The \texttt{circular\_orbit} test loads two white dwarfs on a grid and then orbits
them for a large number of periods, to test conservation of linear momentum,
angular momentum and energy convergence.
    \item The \texttt{evrard\_collapse} test runs the test problem described originally by 
\cite{evrard:1988} and whose results for a grid-based code can be seen in \cite{arepo}. A spherical
distribution of gas obeying a gamma-law equation of state is loaded onto a grid with negligible 
pressure. The gas collapses, rebounds with a shock, and then settles into hydrodynamic equilibrium.
It is a good test of the energy conservation properties of the code.
    \item The \texttt{freefall} test loads two white dwarfs onto a grid and allows them to fall towards
each other under their mutual gravitational influence. We check to see whether the timescale for them
colliding matches the analytical expectation for two point masses.
    \item The \texttt{kelvin\_helmoltz} test runs several varieties of a 2D shearing fluid that exhibits the 
Kelvin-Helmholtz instability. The relevant papers are \cite{robertson:2010}, \cite{arepo}, and \cite{mcnally:2012}.
    \item The \texttt{single\_star\_hse} test loads a single white dwarf on a grid and checks how well 
hydrostatic equilibrium is maintained.
  \end{itemize}
  \item The \texttt{performance} subdirectory examines the scaling and performance properties of CASTRO.
  \begin{itemize}
    \item The \texttt{strong\_scaling} test runs the same problem with a varying number of processors and 
checks the scaling properties.
    \item The \texttt{weak\_scaling} test scales the size of the problem with the number of processors and
checks the scaling properties.
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item The \texttt{binary} subdirectory includes problems that test the binary star setup.
  \begin{itemize}
    \item The \texttt{boundary\_condition\_comparison} test checks the validity of our 
      multipole approximation for the boundary conditions on the Poisson equation. It runs
      the gravity solve for several different choices of the number of expansion coefficients
      and compares the resulting gravitational potential to the exact result.
    \item The \texttt{circular\_orbit} test loads two white dwarfs on a grid and then orbits
      them for a large number of periods, to test conservation of linear momentum,
      angular momentum and energy convergence.
    \item The \texttt{freefall} test loads two white dwarfs onto a grid and allows them to fall towards
      each other under their mutual gravitational influence. We check to see whether the timescale for them
      colliding matches the analytical expectation for two point masses.
  \end{itemize}

  \item The \texttt{single} subdirectory is for tests that only use a single star.
  \begin{itemize}
    \item The \texttt{single\_star\_hse} test loads a single white dwarf on a grid and checks how well 
      hydrostatic equilibrium is maintained.
  \end{itemize}

  \item The \texttt{castro} subdirectory is for running tests in the CASTRO test suite that are relevant
  to issues that the merger problem will face.
  \begin{itemize}
    \item The \texttt{uniform\_cube\_sphere} test is designed to check the convergence
        properties of the Poisson solver. It loads either a sphere or cube of uniform density
        onto the computational domain and then calculates the potential at several different
        spatial resolutions to check if the potential converges
    \item The \texttt{evrard\_collapse} test runs the test problem described originally by 
      \cite{evrard:1988} and whose results for a grid-based code can be seen in \cite{arepo}. A spherical
      distribution of gas obeying a gamma-law equation of state is loaded onto a grid with negligible 
      pressure. The gas collapses, rebounds with a shock, and then settles into hydrodynamic equilibrium.
      It is a good test of the energy conservation properties of the code.
    \item The \texttt{kelvin\_helmoltz} test runs several varieties of a 2D shearing fluid that exhibits the 
      Kelvin-Helmholtz instability. The relevant papers are \cite{robertson:2010}, \cite{arepo}, and \cite{mcnally:2012}.
  \end{itemize}

  \item The \texttt{performance} subdirectory examines the scaling and performance properties of CASTRO.
  \begin{itemize}
    \item The \texttt{strong\_scaling} test runs the same problem with a varying number of processors and 
      checks the scaling properties.
    \item The \texttt{weak\_scaling} test scales the size of the problem with the number of processors and
      checks the scaling properties.
    \item The \texttt{threading} test is useful for determining the optimal number of OpenMP threads for your machine.
    \item The \texttt{load\_balancing} test finds which load balancing strategy makes the most sense for our problem.
  \end{itemize}
\end{itemize}
